REDO Simulating Dwarf Galaxy Evolution with Individual Star Feedback and Chemical Evolution I: Methods and Test Case

### 2017-11-21 main.tex
section 3 finished

\section{Galaxy Initial Conditions}
\label{sec:IC}
The galaxy presented in this work is constructed to be similar to the observed properties of the Local Group dwarf galaxy Leo P \citep{Giovanelli2013,McQuinn2013,McQuinn2015a,McQuinn2015}, but is not intended to be a matched model to this galaxy. Leo P is gas rich ($M_{\rm gas} > M_{*}$) and low metallicity, with $M_{\rm HI} = 8.1\times 10^{5}$~M$_{\odot}$ and $M_{*} = 5.6^{+0.4}_{-1.9} \times 10^{5}$~M$_{\odot}$ \citep{McQuinn2015a} extending to a radius $r_{\rm HI} = 500$~pc, and with $12 + \rm{log(O/H)} = 7.17 \pm 0.04$ \citep{Skillman2013}, or $Z \sim 5.4\times10^{-4}$ adopting $Z_{\odot} = 0.018$ from \citet{Asplund2009}. Our dwarf galaxy is constructed without an initial background stellar population, with a total gas mass of $1.8 \times 10^{6}$~M$_{\odot}$ (or $M_{\rm HI} = 1.35 \times 10^{6}$~M$_{\odot}$) and $Z = 4.3\times 10^{-4}$, comparable to the average $z = 0$ metallicity from the stellar models computed in \citep{McQuinn2015}.

The galaxy initially consists of a smooth, exponential gas disk in hydrostatic equillibrium with a static, background dark matter potential. The gas profile follows \citet{Tonnesen2009} and \citet{Salem2015}, or
\begin{equation}
\rho_{\rm gas} (R,z) = \frac{M_{\rm gas}}{2\pi a^2_{\rm gas}b_{\rm gas}} 0.5^2{\rm sech}\left(\frac{R}{a_{\rm gas}}\right){\rm sech}\left(\frac{z}{b_{\rm gas}}\right)
\end{equation}
where $a_{\rm gas}$ and $b_{\rm gas}$ are the radial and vertical gas disk scale heights, and $M_{\rm gas}$ is approximately 70\% of the total gas mass. We set $a_{\rm gas} = 250$~pc, $b_{\rm gas} = 100$~pc, and a total gas mass of $M_{\rm T,gas} = 2.0\times 10^6$~M$_{\odot}$. We adopt a Burkert \citet{Burkert1995} dark matter potential with $M_{\rm vir} = 3.5^{8} \rm{M_{\odot}}$, $R_{\rm vir}~=~14.3$~kpc and r$_{\rm s} = 370$~pc. This gives a maximum circular velocity $V_{\rm max} = 17.4$~km~s$^{-1}$ at $R_{\rm vmax}~=~1.2$~kpc. These parameters were adopted specifically to match the observed dynamical mass of Leo P interior to 500 pc, or $M_{\rm dyn} (r < 500~\rm{pc}) = 2.7\times 10^{7}$ M$_{\odot}$, and represent virial properties near the minimum halo mass expected for galaxies of this size \citep{Ferrero2012} (need more cite). We will explore the effect of adopting different dark matter potentials within the large range of possible profiles in a future work.

Following the initialization procedure of \citet{Hu2017}, we use artificial supernova driving to generate realistic densities and turbulent properties in the galaxy ISM. This additionally prevents an otherwise uniform collapse of the gas disk. The supernovae explode at a fixed rate of $0.4$~Myr$^{-1}$, corresponding to the SFR obtained given the central \ion{H}{1} surface density and the relation presented in \citep{Roychowdhury2009}. We stop the artificial driving 25~Myr after the first star particle forms. These artificial supernova do not drive chemical evolution of the galaxy; their metal yields correspond to the mean ISM abundances.

>>>>

\section{Galaxy Initial Conditions}
\label{sec:IC}
The galaxy presented in this work is constructed to be similar to the observed properties of the Local Group dwarf galaxy Leo P \citep{Giovanelli2013,McQuinn2013,McQuinn2015a,McQuinn2015}, although it is not intended to be a matched model to this galaxy. Leo P is gas rich ($M_{\rm gas} > M_{*}$) and low metallicity, with $M_{\rm HI} = 8.1\times 10^{5}$~M$_{\odot}$ and $M_{*} = 5.6^{+0.4}_{-1.9} \times 10^{5}$~M$_{\odot}$ \citep{McQuinn2015a} extending to a radius $r_{\rm HI} = 500$~pc, and with $12 + \rm{log(O/H)} = 7.17 \pm 0.04$ \citep{Skillman2013}, or $Z \sim 5.4\times10^{-4} Z_{\odot}$, adopting $Z_{\odot} = 0.018$ from \citet{Asplund2009}. Our dwarf galaxy is constructed without an initial background stellar population, with a total gas mass of $1.8 \times 10^{6}$~M$_{\odot}$ (or $M_{\rm HI} = 1.35 \times 10^{6}$~M$_{\odot}$) and $Z = 4.3\times 10^{-4}$, comparable to the average $z = 0$ metallicity from the stellar models computed in \citet{McQuinn2015}.

The galaxy initially consists of a smooth, exponential gas disk in hydrostatic equillibrium with a static, background dark matter potential. The gas profile follows \citet{Tonnesen2009} and \citet{Salem2015}, with
\begin{equation}
\rho_{\rm gas} (R,z) = \frac{M_{\rm gas}}{2\pi a^2_{\rm gas}b_{\rm gas}} 0.5^2{\rm sech}\left(\frac{R}{a_{\rm gas}}\right){\rm sech}\left(\frac{z}{b_{\rm gas}}\right)
\end{equation}
where $a_{\rm gas}$ and $b_{\rm gas}$ are the radial and vertical gas disk scale heights, and $M_{\rm gas}$ is approximately 70\% of the total gas mass. We set $a_{\rm gas} = 250$~pc, $b_{\rm gas} = 100$~pc, and a total gas mass of $M_{\rm T,gas} = 2.0\times 10^6$~M$_{\odot}$. We adopt a \citet{Burkert1995} dark matter potential with $M_{\rm vir} = 3.5\times 10^{8} \mbox{ M_{\odot}}$, $R_{\rm vir}~=~14.3$~kpc and r$_{\rm s} = 370$~pc. This gives a maximum circular velocity $V_{\rm max} = 17.4$~km~s$^{-1}$ at $R_{\rm vmax}~=~1.2$~kpc. These parameters were adopted specifically to match the observed dynamical mass of Leo P interior to 500 pc, or $M_{\rm dyn} (r < 500~\rm{pc}) = 2.7\times 10^{7}$ M$_{\odot}$, and represent virial properties near the minimum halo mass expected for galaxies of this size \citep{Ferrero2012} (need more cite). We will explore the effect of adopting different dark matter potentials within the large range of possible profiles in a future work.

Following the initialization procedure of \citet{Hu2017}, we use artificial supernova driving to generate realistic initial densities and turbulent properties in the galaxy ISM. This additionally prevents an otherwise uniform collapse of the gas disk 
%mm
   at the beginning of the simulation. These supernovae explode at a fixed rate of $0.4$~Myr$^{-1}$, corresponding to the SFR obtained given the central \ion{H}{1} surface density and the relation presented in \citep{Roychowdhury2009}. We stop the artificial driving 25~Myr after the first star particle forms. These artificial supernovae do not drive chemical evolution of the galaxy; their metal yields correspond to the mean ISM abundances. 
%mm
    We do not include any other effects from the stellar population that would have caused these   
    supernovae.
